---
title: "Put your title here"
author: "John Smith"
date: "July 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task
Your task is to perform a short regression analysis, investigating the relationship between two variables on the ``mtcars`` dataset. You will need to:

1. Load the data
2. Plot the data (e.g. ``mpg`` versus ``wt``)
3. Write up the linear model as an equation (try using latex!)
4. Fit the model and check your modelling assumptions.
5. Plot and interpret the result.
6. Write a conclusion

Complete your an analysis in Rmarkdown document with the following headings:

- Introduction
- Data
- Method
- Results
- Conclusion

Additionally, you should attach a bibliography using a ``.bib`` file containing your references.

Example of how to read in data in R below.

```{r load_data}
data("mtcars")
```


A template structure you can follow below.

## Introduction



## Data



## Exploratory data analysis



## Model



## Results



## Conclusions



## Bibliography

